---
title: "Proposal"
---
```{r}
library(gt)
library(ggplot2)
roles <- read.csv("..//..//data//whoseresponsible.csv") 
```
## "It was awful, and such small portions!": a reflection on time to finish and review scores for modern video games
### Merce Lutzker and Elina Poll {-}
::: {.callout-note title="Project Description"}
We will compare datasets on various contemporary video games regarding aggegregate consumer ratings on the website Metacritic, and average time to complete the game according to HowLongToBeat, another consumer-sourced aggregator to analyze their correlation. Or in short, how game length affects game enjoyment or rating

:::

::: {.callout-note title="Responsibility Plan"}
```{r}
roles |>
  gt()
```


:::

::: {.callout-note title="Inspirations"}
With us both being avid fans of video games alike, a growing trend in the industry is to add more padding in order to prolong gameplay. While some despise and others love the tactic, we were curious if a higher average playtime would result in higher review aggregate scores.
:::
